\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

\vspace*{6pt}
\subsection{{Protocol Engineer}\hfill May 2025 - February 2026}
\subtext{Somnia Foundation/Virtual Society Foundation}
\begin{zitemize}
    \item Core contributor to Somnia L1 node (C++), focusing on consensus mechanisms, networking protocols, and performance optimization across the client stack.
    \item Built compiler optimizations and database indexing improvements to reduce block processing latency and increase transaction throughput.
    \item Designed and implemented native oracle service architecture including Solidity smart contracts, off-chain worker nodes, and data verification systems for bringing external data on-chain.
\end{zitemize}

\vspace*{6pt}
\subsection{{Protocol Engineer}\hfill June 2024 - May 2025}
\subtext{Community Labs/Astro Labs}
\begin{zitemize}
    \item Architected and built cross-chain bridge connecting Ethereum, Arweave, and AO networks, handling secure multi-network asset and data transfers.
    \item Implemented bridge components including Solidity smart contracts, oracle infrastructure, and MPC-based signing nodes in C++ for distributed key management.
    \item Designed security mechanisms for cross-chain message validation and replay attack prevention.
\end{zitemize}

\vspace*{3pt}
\subsection{{Internship}\hfill June 2023 - September 2023}
\subtext{Nethermind}
\begin{zitemize}
    \item Contributed to Ethereum client development discussions and gained exposure to professional blockchain engineering practices.
\end{zitemize}

\vspace*{1pt} 
\subsection{{Blockchain Researcher}\hfill September 2022 - September 2023}
\begin{zitemize}
    \item Research on blockchain consensus protocols for master's thesis (research grant awarded); published academic article on distributed systems.
\end{zitemize}

\vspace*{1pt} 
\subsection{{Software Engineer (Freelance / Contract)}\hfill October 2019 - September 2022}
\begin{zitemize}
  \item Developed and deployed production-grade Solana smart contracts and decentralized applications using Rust and the Anchor framework.
  \item Engineered high-performance backend automation tools, bots, and API services for international clients using Rust, Go, and Python.
  \item Collaborated with clients to define technical requirements and deliver end-to-end solutions from design to production deployment.
\end{zitemize}

\end{document}
