\vspace*{10pt}

\documentclass[a4paper, 12pt]{article}
\begin{document}

\subsection{Research on Blockchain Consensus Protocols (Master's Thesis)}
\begin{itemize}
  \item Developed blockchain consensus protocols for Tezos, Proof of Work and Authority. Created tools, such as Bootstrapper and Live Testing Tool, using OCaml to enhance protocol creation, performance evaluation.
\end{itemize}

\subsection{Arrow Distributed Directory Protocol}
\begin{itemize}
  \item Implemented a distributed directory protocol node in Go, featuring a live visualization tool for network state and access control in distributed systems.
\end{itemize}

\subsection{Distributed Database/Filesystem}
\begin{itemize}
  \item Created a distributed database and filesystem using Rust and Libp2p, focusing on efficient data storage and retrieval in a peer-to-peer network.
\end{itemize}

\subsection{On-disk Key Value Database}
\begin{itemize}
  \item Engineered a key-value disk database in C, utilizing B-trees for optimized data management and access.
\end{itemize}

\subsection{Language Design/Compilers}
\begin{itemize}
  \item Developed Garbage Lisp, a Go-based interpreter and an OCaml-based Pascal to Assembly (X\_86) compiler, demonstrating expertise in language design, parsing, and code generation.
\end{itemize}

\subsection{Ethereum/EVM/Solidity}
\begin{itemize}
  \item Developed in Solidity a DEX with liquidity pool mechanics for token swaps and a game leveraging smart contracts for interactive gameplay, both deployed on the EVM. 
\end{itemize}


\subsection{Solana}
\begin{itemize}
  \item Built a fully decentralized social network leveraging TypeScript and IPFS, and implemented a token holding platform with incentives, both utilizing Solana's blockchain capabilities.
\end{itemize}



\end{document}
